Local Search, Brute-Force and Recursion for Selection Operator\thanks{This work was not supported by Velbazhd Software LLC and Bulgarian Ministry of Education and Science.}

### 2020-04-11 Local-Search-Brute-Force-and-Recursion-for-Selection-Operator/paper.tex
Most of the introduction was written.

>>>>

Selecting parents for mating can be done according many different strategies. The most important target of successful mating is to select as better individuals as possible more often with the hope that they will produce even better offspring. Selecting parents at random will lead to a very slow convergence of the optimization process. The proportional selection is one of the first improvements in the selection process. The idea behind it is that each individual receives a crossover chance proportional to its fitness value. Tournament selection is another selection strategy in which by competition between a subset of individuals only winners are nominated for mating. Rank selection on the other side uses ranking of individuals in order to determine their chances for mating. Boltzmann selection uses simulated annealing. In this strategy, winners are nominated after a predetermined number of Boltzmann experiments.

There are many hybrid implementations of the above listed selection strategies. This research proposes a local search extension of the brute-force element in the recursive selection proposed by Tomov, Zankinski, and Balabanov \cite{}. A hierarchy of sub-generations is generated and the best-fitted individuals are selected with recursive descent. On each level of recursion single brute-force searching is applied and only one individual is promoted to a higher level. The newly proposed modification applies brute-force search as many times as there is an improvement of the findings, which in fact is a local search extension.
